---
title: "p8105_hw6_ga2612"
author: "Lupe Antonio"
date: "12/1/2023"
output:
  github_document:
    toc: TRUE
---

```{r setup, include=FALSE, message = FALSE}
library(tidyverse)
library(broom)
```

## Problem 1

```{r, message = FALSE}
#loading data
homicide_data <- read_csv('data_hw6/homicide_data.csv') %>%
  mutate(
    city_state = str_c(city, state, sep = ', '),
    #unsolved == 0, solved == 1
    resolution = case_when(
      disposition == 'Closed without arrest' ~ 0,
      disposition == 'Open/No arrest' ~ 0,
      disposition == 'Closed by arrest' ~ 1),
    #making victime_age numeric
    victim_age = as.numeric(victim_age)) %>%
  #excluding cities
  filter(city_state != 'Dallas, TX',
         city_state != 'Phoenix, AZ',
         city_state != 'Kansas City, MO',
         city_state != 'Tulsa, AL',
        #filtering victim_race
        victim_race == 'White' | victim_race == 'Black')
```


```{r, message = FALSE}
baltimore_data <- homicide_data %>%
  filter(city_state == 'Baltimore, MD')

#fitting glm model
baltimore_logistic <- baltimore_data %>%
  glm(resolution ~ victim_age + victim_sex + victim_race,
    data = ., family = binomial())


#obtaining estimate
baltimore_logistic %>%
  tidy() %>%
  filter(term == 'victim_sexMale') %>%
  mutate(adj_OR = exp(estimate),
         OR_low = exp(estimate - 1.96 * std.error),
         OR_upper = exp(estimate + 1.96 * std.error)) %>%
  select(term, adj_OR, OR_low, OR_upper)

#obtaining confidence interval for checking purposes
exp(confint(baltimore_logistic)['victim_sexMale', ])
```


Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}

```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.




## Problem 2

```{r}
#loading data
weather_df <- 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

The boostrap is helpful when you’d like to perform inference for a parameter / value / summary that doesn’t have an easy-to-write-down distribution in the usual repeated sampling framework. We’ll focus on a simple linear regression with tmax as the response with tmin and prcp as the predictors, and are interested in the distribution of two quantities estimated from these data:

r̂ 2
log(β̂ 1∗β̂ 2)
Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words. Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2
 and log(β̂ 0∗β̂ 1)
. Note: broom::glance() is helpful for extracting r̂ 2
 from a fitted regression, and broom::tidy() (with some additional wrangling) should help in computing log(β̂ 1∗β̂ 2)


```{r}
#
```

